---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# ggpolar

<!-- badges: start -->
<!-- badges: end -->

ggpolar supplies a few ggplot2 facilities to plot data in polar coordinate on a cartesian layer.

## Installation

By now, ggpolar has not been submitted to cran. You can try the development version from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("microly/ggpolar")
```
## Usage

1.You can map radius and theta to a layer directly.

```{r map_radius_theta}
library(tibble)
library(ggplot2)
library(ggpolar)

polar_data <- tibble(theta = 1:360, radius = theta)

# use StatPolar
ggplot(polar_data) + 
    geom_path(aes(p_theta = theta, p_radius = radius), stat = "polar")

# use with_polar, which is a layer modifier
ggplot(polar_data) + 
    with_polar(geom_path(aes(p_theta = theta, p_radius = radius)))

# the way to suppress the warning "Ignoring unknown aesthetics: p_theta, p_radius":
ggplot(polar_data, aes(p_theta = theta, p_radius = radius)) + 
    with_polar(geom_path())
```

2.You can also translate and(or) rotate the data.

```{r translate_rotate}
ggplot(polar_data, aes(p_theta = theta, p_radius = radius)) + 
    with_polar(geom_path(),
               geom_path(aes(polar_x = 200, polar_y = 200, polar_theta0 = 180)))
```


3.Data can be interpolated automatically, so you can draw arcs and sectors as easily as draw lines and polygons.

```{r interpolation}
# you define the start and end points
polar_data2 <- tibble(theta = c(0,90), radius = 1)

# ggpolar will automatically interpolate other points.

# an arc example
ggplot(polar_data2, aes(p_theta = theta, p_radius = radius)) + 
    with_polar(geom_path(), interpolate = TRUE) + 
    coord_equal()

# a sector example
ggplot(polar_data2, aes(p_theta = theta, p_radius = radius)) + 
    with_polar(geom_polygon(), interpolate = TRUE, add_origin = TRUE) + 
    coord_equal()

# ggpolar can even make the supplement geometry for you! 
ggplot(polar_data2, aes(p_theta = theta, p_radius = radius)) + 
    with_polar(geom_polygon(), interpolate = TRUE, add_origin = TRUE) +
    with_polar(geom_polygon(fill = "red"), interpolate = TRUE, 
               supplement = TRUE, add_origin = TRUE) +
    coord_equal()
```

4.With the help of some layer functions (geom_plar_axis, geom_polar_ring and geom_polar_bar), you can draw the polar coordinates based plots (eg. radar plot, pie chart and Nightingale rose diagram) in a more intuitively way.

```{r layer_functions}

# I will add some examples later.
```
