---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# ggpolar

<!-- badges: start -->
<!-- badges: end -->

ggpolar supplies a few ggplot2 facilities to plot the data in polar coordinate on the layer of cartesian coordinate.

## Installation

By now, ggpolar has not been submitted to cran. You can try the development version from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("microly/ggpolar")
```
## Usage

1.You can map radius and theta data to the plot directly.

```{r map_radius_theta}
library(tibble)
library(ggplot2)
library(ggpolar)

polar_data <- tibble(theta = 1:360, radius = theta)

# use StatPolar
ggplot(polar_data) + 
    geom_path(aes(p_theta = theta, p_radius = radius), stat = "polar")

# use with_polar, which is a layer modifier
ggplot(polar_data) + 
    with_polar(geom_path(aes(p_theta = theta, p_radius = radius)))

# the way to suppress the warning "Ignoring unknown aesthetics: p_theta, p_radius":
ggplot(polar_data, aes(p_theta = theta, p_radius = radius)) + 
    with_polar(geom_path())
    
```

2.You can also translate and(or) rotate the data before the mapping process.


3.Data can be interpolated automatically, so you can draw arcs and sectors as easily as draw lines and polygons.


4.With the help of some layer functions (geom_plar_axis, geom_polar_ring and geom_polar_bar), you can draw the polar coordinate based plots (eg. radar plot, pie plot and Nightingale rose diagram ) in a more intuitively way.
